Maxwell: bringing cloud-powered electromagnetic simulations to Matlab

### 2012-10-22 presentations/maxwell_documentation/pres.tex
Format of group presentation set.
Going on pres.

\documentclass[landscape]{foils}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}

\title{Maxwell: bringing cloud-powered electromagnetic simulations to Matlab}
\author{}
\MyLogo{Jesse Lu, Jelena Vuckovic group, Stanford University}
\date{}

@@

\BIT \itemsep -1pt
\item Quick-start
\item How Maxwell works
\item How the frequency-domain solver works
\item Examples
\EIT

@@

\oursection{Problem Statement}
% \oursection{Plan}
% \BIT
% \item Software to solve $A^{-1}z$.
% \item Adjoint
% \EIT
\end{document}

>>>>

\documentclass[landscape]{foils}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{pstricks}
\usepackage{pst-grad}
\input defs.tex
\raggedright
\special{! TeXDict begin /landplus90{true}store end }
\renewcommand{\oursection}[1]{
\foilhead[-1.0cm]{#1}
}

\title{Maxwell: bringing cloud-powered electromagnetic simulations to Matlab}
\author{Advanced user interface tutorial}
\MyLogo{Jesse Lu, Jelena Vuckovic group, Stanford University}
\date{}

@@

\BIT \itemsep -1pt
\I  Quick-start
\I  How Maxwell uses the cloud (EC2)
\I  How Maxwell solves electromagnetics
\I  Examples
\EIT

@@

\oursection{Definitions}
\BIT
\I  What is Maxwell?
    \BIT
    \I  a Matlab toolset 
    \I  that uses Amazon's Elastic Compute Cloud (EC2)
    \I  to solve frequency-domain electromagnetic simulations.
    \EIT
\I  Maxwell provides two user interfaces: advanced and other
    \BIT
    \I  advanced:
    \I  other:
    \EIT
\I  This presentation covers the advanced interface 
\EIT

\oursection{Quick-start}
\BIT \I Sign up at \EIT
\begin{verbatim}
% Download maxwell.m
>> urlwrite('m.lightlabs.co', 'maxwell.m');

% Provide AWS credentials and launch a 2-node cluster.
>> maxwell.aws_credentials('aws-access-id', 'aws-secret-key');
>> maxwell.launch('cluster-name', 2);

% Run a 1-node simulation.
>> [E, H] = maxwell.solve('cluster-name', 1, ...);

% Terminate cluster
>> maxwell.terminate('cluster-name');
\end{verbatim}

{Wait, what just happened?}
\BIT
\I  \verb=urlwrite()= downloaded the advanced interface for Maxwell,
\I  \verb=maxwell.aws_credentials()= provided the AWS credentials that
\I  \verb=maxwell.launch()= needed to create a cluster on EC2.
\I  \verb=maxwell.solve()= solved the electromagnetic simulation on
    the cluster and downloaded the resulting electromagnetic fields, and
\I  \verb=maxwell.terminate()= terminated the EC2 cluster.
\EIT

\oursection{How Maxwell uses the cloud (EC2)}

\newpage
\begin{center}

\psset{unit=2cm}
\begin{pspicture}(6,4)(-5,-2)
\psset{gridcolor=green, subgridcolor=yellow}
    % \let\psgrid\relax
    \psgrid
    \psframe[linestyle=none,
            fillstyle=gradient,
            gradbegin=white,gradend=lightgray,
            gradmidpoint=0.5,
            gradangle=0](0,-1.5)(6,3.5)
    \psline[linestyle=dotted](0,3)(0,-1)
    \rput(-2.5,3.5){Matlab}
    \rput(3,3.5){Amazon EC2}

    \psline(-1.5,2.5)(3,2.5)
    \psline{->}(3,2.5)(3,2)

\end{pspicture}
\end{center}
\BIT
\I  Wait, what's going on here?
\EIT

\oursection{How Maxwell solves electromagnetics}
\oursection{Examples}

\end{document}
